\cvsection{Grants and Supports}

% \publicationstyle{\underline{Underline}---Myself}

\publicationstyle{I have acquired research funding that totals \$1,685,843 at William \& Mary. }

\begin{cventries}

  \vspace{0.1cm}

\cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{Advancing Tools and Resources for the AMD ROCm Platform}}
    {\$100,000}
    {Dec. 2024}
    {}
    \vspace{-0.5cm}

\cvgrantentry
    {\textit{NSF, CAREER, Sole PI}}
    {\textbf{CAREER: Towards Next-Generation Human-in-the-Loop and Human-over-the-Loop Computer Architecture Performance Analysis Infrastructure}}
    {\$598,555}
    {4/1/2025-3/31/2030}
    {}
    \vspace{-0.5cm}


  \cvgrantentry
    {\textit{NSF, SHF Core, Medium}
    \linebreak
    \textit{PI: \underline{Yifan Sun} (lead institution lead PI), Adwait Jog, Sreepathi Pai}}
    {\textbf{Enabling GPU Performance Simulation for Large-Scale Workloads with Lightweight Simulation Methods}}
    {\$1,133,743; my~share=\$376,249}
    {5/1/2024-4/30/2028}
    {}
    \vspace{-0.5cm}


  \cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{Binary Instrumentation for GPU Programs on AMD Platforms.}}
    {\$50,000}
    {Dec. 2023}
    {}
    \vspace{-0.5cm}

  \cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{HIP Development on AMD ROCm Platform.}}
    {\$50,000}
    {Dec. 2023}
    {}
    \vspace{-0.5cm}

  \cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{The Methods of Profiling and Tracing of GPU Programs Running on AMD ROCm Platforms.}}
    {\$44,000}
    {May. 2023}
    {}
    \vspace{-0.5cm}


  \cvgrantentry
    {\textit{NSF, CRII, Sole PI}}
    {\textbf{Building Explainable Architecture with Simulation and Visualization Techniques}}
    {\$175,000}
    {5/1/2023-4/30/2026}
    {}
    \vspace{-0.5cm}



  \cvgrantentry
    {\textit{NSF, CCRI (later renamed as CIRC), Planning-C}
    \linebreak
    \textit{PI: \underline{Yifan Sun} (lead institution lead PI), Katherine E. Issacs (University of Utah)}}
    {\textbf{Enabling Computer Architecture as a Service}}
    {\$100,000; my~share=\$72,369}
    {3/15/2023-2/28/2026}
    {}
    \vspace{-0.5cm}
  
  \cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{AMD ROCm and HIP Platform Development}}
    {\$60,000 + 2x AMD MI100 GPU}
    {Mar. 2022}
    {}
    \vspace{-0.5cm}
  
  \cvgrantentry
    {\textit{Neocortex, Pittsburgh Supercomputing Center \linebreak PI: Huajie Shao, \underline{Yifan Sun}}}
    {\textbf{Exploring Interpretable Deep Learning from Information Theoretic Perspective:  Modeling and Applications}}
    {Access to Cerebras Wafer-Scale Computing Devices}
    {Feb. 2022}
    {}
    \vspace{-0.5cm}
  
  \cvgrantentry
    {\textit{Coastal Virginia Center for Cyber Innovation (COVA CCI) \linebreak PI: Dmitry Evtyushkin, Co-PI: Evgenia Smirni, \underline{Yifan Sun}, Adwait Nadkarni}}
    {\textbf{Developing Infrastructure for Advancing Research and Teaching \linebreak in Security and Reliability}}
    {\$79,670 for equipment shared by the department}
    {Dec. 2021}
    {}
    \vspace{-0.5cm}

  \cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{AMD ROCm and HIP Platform Development}}
    {\$40,000}
    {Sep. 2021}
    {}
    \vspace{-0.5cm}
    
  \cvgrantentry
    {\textit{AMD, Gift, Sole PI}}
    {\textbf{General-Purpose Computing with AMD Graphics Processors}}
    {\$40,000}
    {Apr. 2021}
    {}
    \vspace{-0.5cm}
    
\internal{
  \cvgrantentry
    {\textit{NSF, CCRI, } \textcolor{red}{\textbf{Not Funded}}}
    {\textbf{A Community Ecosystem for Accelerator Modeling and Analytics}}
    {$\approx$2M, W\&M $\approx$1.5M}
    {Jan. 2021}
    {}
    \vspace{-0.5cm}
}


\end{cventries}
