\cvsection{Publications}

\publicationstyle{\underline{Underline}---Myself}

\publicationstyle{\uwave{Wavy Underline}---My W\&M Student Advisee}

\cvsubsection{Peer-Reviewed Conference Papers}

    \begin{cvpublications}

        \cvpublication{Wenhan Lyu, Yimeng Wang, \selfname{Yifan Sun}, and Yixuan Zhang. 2025. \pubtitle{Will Your Next Pair Programming Partner Be Human? An Empirical Evaluation of Generative AI as a Collaborative Teammate in a Semester-Long Classroom Setting}. In Proceedings of the Twelfth ACM Conference on Learning @ Scale (L@S '25). Association for Computing Machinery, New York, NY, USA, 83–94. https://doi.org/10.1145/3698205.3729544
        [Acceptance Rate 18/84 $\approx$ 21.4\%]
        }

        \cvpublication{\uwave{Ying Li}, Yuhui Bao, Gongyu Wang, Xinxin Mei, Pranav Vaid, Anandaroop Ghosh, Adwait Jog, Darius Bunandar, Ajay Joshi, and \selfname{Yifan Sun}. 2025. \pubtitle{TrioSim: A Lightweight Simulator for Large-Scale DNN Workloads on Multi-GPU Systems}. In Proceedings of the 52nd Annual International Symposium on Computer Architecture (ISCA '25). Association for Computing Machinery, New York, NY, USA, 1524–1538. https://doi.org/10.1145/3695053.3731082
        [Acceptance Rate 132/570 $\approx$ 23.2\%]
        }

        \cvpublication{Amel Fatima, Yang Yang, \selfname{Yifan Sun}, Rachata Ausavarungnirun, and Adwait Jog. 2025. \pubtitle{NetCrafter: Tailoring Network Traffic for Non-Uniform Bandwidth Multi-GPU Systems}. In Proceedings of the 52nd Annual International Symposium on Computer Architecture (ISCA '25). Association for Computing Machinery, New York, NY, USA, 1064–1078. https://doi.org/10.1145/3695053.3731040 
        [Acceptance Rate 132/570 $\approx$ 23.2\%]
        }

        \cvpublication{Changxi Liu, Miao Yu, \selfname{Yifan Sun}, and Trevor E. Carlson. 2025. \pubtitle{The Sparsity-Aware LazyGPU Architecture}. In Proceedings of the 52nd Annual International Symposium on Computer Architecture (ISCA '25). Association for Computing Machinery, New York, NY, USA, 1020–1034. https://doi.org/10.1145/3695053.3731009 
        [Acceptance Rate 132/570 $\approx$ 23.2\%]
        }

        \cvpublication{Matin Raayai-Ardakani, Andrew Nguyen, Ivan Rosales, \uwave{Daoxuan Xu}, Yuwei Sun, \selfname{Yifan Sun}, David Kaeli, and Norman Rubin. 2025. \pubtitle{Luthier: A Dynamic Binary Instrumentation Framework Targeting AMD GPUs}. In Proceedings of the 2025 IEEE International Symposium on Performance Analysis of Systems and Software (ISPASS), May 11-13, 2025. 137–149. Ghent, Belgium. https://doi.org/10.1109/ISPASS64960.2025.00022
        [Acceptance Rate 28/99 $\approx$ 28\%]
        }

        
        
        
        \cvpublication{Ali Mosallaei, Katherine E. Isaacs, and \selfname{Yifan Sun}. 2024. \pubtitle{Looking into the Black Box: Monitoring Computer Architecture Simulations in Real-Time with AkitaRTM}. In 2024 57th IEEE/ACM International Symposium on Microarchitecture (MICRO '24). IEEE, 780–794.  https://doi.org/10.1109/MICRO61859.2024.00063 [Acceptance Rate 113/ 489 $\approx$ 22.7\%]}

         \cvpublication{Wenhan Lyu, Yimeng Wang, Tingting (Rachel) Chung, \selfname{Yifan Sun}, and Yixuan Zhang. 2024. \pubtitle{Evaluating the Effectiveness of LLMs in Introductory Computer Science Education: A Semester-Long Field Study}. In Proceedings of the Eleventh ACM Conference on Learning @ Scale (L@S '24). Association for Computing Machinery, New York, NY, USA, 63–74. https://doi.org/10.1145/3657604.3662036 [Acceptance rate: 22/ 90 $\approx$ 24.4\%] }
    

        \cvpublication{Yichen Luo, Daoxuan Xu, Gang Zhou, \selfname{Yifan Sun}, and Sidi Lu. 2024. \pubtitle{Impact of Raindrops on Camera-Based Detection in Software-Defined Vehicles}. In 2024 IEEE International Conference on Mobility, Operations, Services and Technologies (MOST '24). IEEE, 193–205.  https://doi.org/10.1109/MOST60774.2024.00028}
    
        

        \cvpublication{\uwave{Ying Li}, \selfname{Yifan Sun}, and Adwait Jog. 2023. \pubtitle{Path Forward Beyond Simulators: Fast and Accurate GPU Execution Time Prediction for DNN Workloads}. In Proceedings of the 56th Annual IEEE/ACM International Symposium on Microarchitecture (MICRO '23). Association for Computing Machinery, New York, NY, USA, 380–394. \\ 
        https://doi.org/10.1145/3613424.3614277 
        [Acceptance rate: 101/424 $\approx$ 23.8\%] }

        \cvpublication{Changxi Liu, \selfname{Yifan Sun}, and Trevor E. Carlson. 2023. \pubtitle{Photon: A Fine-grained Sampled Simulation Methodology for GPU Workloads}. In Proceedings of the 56th Annual IEEE/ACM International Symposium on Microarchitecture (MICRO '23). Association for Computing Machinery, New York, NY, USA, 1227–1241. https://doi.org/10.1145/3613424.3623773 
        [Acceptance rate: 101/424 $\approx$ 23.8\%] }

        \cvpublication{\faTrophy \hspace{1pt} \textbf{[Best Paper Award (Top 1\%)] }
        Yixuan Zhang, Joseph D Gaggiano, Nutchanon Yongsatianchot, Nurul M Suhaimi, Miso Kim, \selfname{Yifan Sun}, Jacqueline Griffin, and Andrea G Parker. 2023. \pubtitle{What Do We Mean When We Talk about Trust in Social Media? A Systematic Review}. In Proceedings of the 2023 CHI Conference on Human Factors in Computing Systems (CHI '23). Association for Computing Machinery, New York, NY, USA, Article 670, 1–22. \\https://doi.org/10.1145/3544548.3581019 
        [Acceptance rate: 879/3182 $\approx$ 27.6\%] 
        }
        
        \cvpublication{Yixuan Zhang, \selfname{Yifan Sun}, Joseph D. Gaggiano, Neha Kumar, Clio Andris, and Andrea G. Parker. 2023. \pubtitle{Visualization Design Practices in a Crisis: Behind the Scenes with COVID-19 Dashboard Creators}. IEEE Transactions on Visualization and Computer Graphics 29, 1 (2023), 1037–1047.  https://doi.org/10.1109/TVCG.2022.3209493. 
        [Acceptance rate: 122/ 460 $\approx$ 26.5\%]}

        \cvpublication{Yuhui Bao, \selfname{Yifan Sun}, Zlatan Feric, Michael Tian Shen, Micah Weston, José L. Abellán, Trinayan Baruah, John Kim, Ajay Joshi, and David Kaeli. 2023. \pubtitle{NaviSim: A Highly Accurate GPU Simulator for AMD RDNA GPUs}. In Proceedings of the International Conference on Parallel Architectures and Compilation Techniques (PACT '22). Association for Computing Machinery, New York, NY, USA, 333–345. https://doi.org/10.1145/3559009.3569666 [Acceptance rate: 50/ 118 $\approx$ 42.4\%]}

        \cvpublication{Yixuan Zhang, Nurul Suhaimi, Nutchanon Yongsatianchot, Joseph D Gaggiano, Miso Kim, Shivani A Patel, \selfname{Yifan Sun}, Stacy Marsella, Jacqueline Griffin, and Andrea G Parker. 2022. \pubtitle{Shifting Trust: Examining How Trust and Distrust Emerge, Transform, and Collapse in COVID-19 Information Seeking}. In Proceedings of the 2022 CHI Conference on Human Factors in Computing Systems (CHI '22). Association for Computing Machinery, New York, NY, USA, Article 78, 1–21. https://doi.org/10.1145/3491102.3501889 [Top 12.5\%; Acceptance rate: 638/ 2597 $\approx$ 24.6\%]} 

        \cvpublication{\selfname{Yifan Sun}, Yixuan Zhang, Ali Mosallaei, Michael D. Shah, Cody Dunne, and David Kaeli. 2021. \pubtitle{Daisen: A Framework for Visualizing Detailed GPU Execution}. Computer Graphics Forum 40, 3 (2021), 239–250.  \\https://doi.org/10.1111/cgf.14303 [Acceptance Rate $\approx$ 26.0\%]}

        
        \cvpublication{Yixuan Zhang, \selfname{Yifan Sun}, Lace Padilla, Sumit Barua, Enrico Bertini, and Andrea G Parker. 2021. \pubtitle{Mapping the Landscape of COVID-19 Crisis Visualizations}. In Proceedings of the 2021 CHI Conference on Human Factors in Computing Systems (CHI '21). Association for Computing Machinery, New York, NY, USA, Article 608, 1–23. \\ https://doi.org/10.1145/3411764.3445381 [Acceptance rate $\approx$ 26.3\%]}

        \cvpublication{Trinayan Baruah, Kaustubh Shivdikar, Shi Dong, \selfname{Yifan Sun}, Saiful A. Mojumder, Kihoon Jung, José L. Abellán, Yash Ukidave, Ajay Joshi, John Kim, and David Kaeli. 2021. \pubtitle{GNNMark: A Benchmark Suite to Characterize Graph Neural Network Training on GPUs}. In 2021 IEEE International Symposium on Performance Analysis of Systems and Software (ISPASS '21). IEEE, 13–23.  https://doi.org/10.1109/ISPASS51385.2021.00013 [Acceptance rate $\approx$ 36.9\%]}

        \cvpublication{Trinayan Baruah, \selfname{Yifan Sun}, Saiful A. Mojumder, José L. Abellán, Yash Ukidave, Ajay Joshi, Norman Rubin, John Kim, and David Kaeli. 2020. \pubtitle{Valkyrie: Leveraging Inter-TLB Locality to Enhance GPU Performance}. In Proceedings of the ACM International Conference on Parallel Architectures and Compilation Techniques (PACT '20). Association for Computing Machinery, New York, NY, USA, 455–466. https://doi.org/10.1145/3410463.3414639 [Acceptance rate $\approx$ 25.9\%]}

        
        \cvpublication{\faTrophy \hspace{1pt} \textbf{[Best Paper Honorable Mention (\textless 5\%)]} Omid Mohaddesi, \selfname{Yifan Sun}, Rana Azghandi, Rozhin Doroudi, Sam Snodgrass, Ozlem Ergun, Jacqueline Griffin, David Kaeli, Stacy Marsella, and Casper Harteveld. 2020. \pubtitle{Introducing Gamettes: A Playful Approach for Capturing Decision-Making for Informing Behavioral Models}. In Proceedings of the 2020 CHI Conference on Human Factors in Computing Systems (CHI '20). Association for Computing Machinery, New York, NY, USA, 1–13. https://doi.org/10.1145/3313831.3376571 [Acceptance rate $\approx$ 24.3\%]}

    
        \cvpublication{Trinayan Baruah, \selfname{Yifan Sun}, Ali Tolga Dinçer, Saiful A. Mojumder, José L. Abellán, Yash Ukidave, Ajay Joshi, Norman Rubin, John Kim, and David Kaeli. 2020. \pubtitle{Griffin: Hardware-Software Support for Efficient Page Migration in Multi-GPU Systems}. In 2020 IEEE International Symposium on High Performance Computer Architecture (HPCA '20). IEEE, 596–609.  https://doi.org/10.1109/HPCA47549.2020.00055 [Acceptance rate $\approx$ 19.4\%]}

        

        \cvpublication{\selfname{Yifan Sun}, Trinayan Baruah, Saiful A. Mojumder, Shi Dong, Xiang Gong, Shane Treadway, Yuhui Bao, Spencer Hance, Carter McCardwell, Vincent Zhao, Harrison Barclay, Amir Kavyan Ziabari, Zhongliang Chen, Rafael Ubal, José L. Abellán, John Kim, Ajay Joshi, and David Kaeli. 2019. \pubtitle{MGPUSim: enabling multi-GPU performance modeling and optimization}. In Proceedings of the 46th International Symposium on Computer Architecture (ISCA '19). Association for Computing Machinery, New York, NY, USA, 197–209. https://doi.org/10.1145/3307650.3322230 [Acceptance rate $\approx$ 17.0\%]}
        
        
        \cvpublication{Mohammad Khavari Tavana, \selfname{Yifan Sun}, Nicolas Bohm Agostini, and David Kaeli. 2019. \pubtitle{Exploiting Adaptive Data Compression to Improve Performance and Energy-Efficiency of Compute Workloads in Multi-GPU Systems}. In 2019 IEEE International Parallel and Distributed Processing Symposium (IPDPS '19). IEEE, 664–674. \\ https://doi.org/10.1109/IPDPS.2019.00075 [Acceptance rate $\approx$ 27.7\%]}

        \cvpublication{Saiful A. Mojumder, Marcia S. Louis, \selfname{Yifan Sun}, Amir Kavyan Ziabari, José L. Abellán, John Kim, David Kaeli, and Ajay Joshi. 2018. \pubtitle{Profiling DNN Workloads on a Volta-based DGX-1 System}. In 2018 IEEE International Symposium on Workload Characterization (IISWC '18). IEEE, 122–133.  https://doi.org/10.1109/IISWC.2018.8573521 [Acceptance rate $\approx$ 36.2\%]}

        
        \cvpublication{Rozhin Doroudi, Rana Azghandi, Zlatan Feric, Omid Mohaddesi, \selfname{Yifan Sun}, Jacqueline Griffin, Ozlem Ergun, David Kaeli, Pedro Sequeira, Stacy Marsella, and Casper Harteveld. 2018. \pubtitle{An Integrated Simulation Framework for Examining Resiliency in Pharmaceutical Supply Chains Considering Human Behaviors}. In 2018 Winter Simulation Conference (WSC '18). IEEE, 88–99.  https://doi.org/10.1109/WSC.2018.8632387 [Acceptance rate $\approx$ 70.4\%]}

        
        \cvpublication{\selfname{Yifan Sun}, Saoni Mukherjee, Trinayan Baruah, Shi Dong, Julian Gutierrez, Prannoy Mohan, and David Kaeli. 2018. \pubtitle{Evaluating Performance Tradeoffs on the Radeon Open Compute Platform}. In 2018 IEEE International Symposium on Performance Analysis of Systems and Software (ISPASS '18). IEEE, 209–218. \\ https://doi.org/10.1109/ISPASS.2018.00034  [Acceptance rate $\approx$ 31.3\%]}
        
        \cvpublication{\faTrophy \hspace{1pt} \textbf{[Best Paper Award]} Shi Dong, Xiang Gong, \selfname{Yifan Sun}, Trinayan Baruah, and David Kaeli. 2018. \pubtitle{Characterizing the Microarchitectural Implications of a Convolutional Neural Network (CNN) Execution on GPUs}. In Proceedings of the 2018 ACM/SPEC International Conference on Performance Engineering (ICPE '18). Association for Computing Machinery, New York, NY, USA, 96–106. https://doi.org/10.1145/3184407.3184423 [Acceptance rate $=$ 24.0\%]}
        
        \cvpublication{Trinayan Baruah, \selfname{Yifan Sun}, Shi Dong, David Kaeli, and Norm Rubin. 2018. \pubtitle{Airavat: Improving Energy Efficiency of Heterogeneous Applications}. In 2018 Design, Automation \& Test in Europe Conference \& Exhibition (DATE '18). IEEE, 731–736. DOI: https://doi.org/10.23919/DATE.2018.8342104 [Acceptance rate $\approx$ 24.2\%]}
        
        \cvpublication{\faTrophy \hspace{1pt} \textbf{[Best Paper Candidate]} \selfname{Yifan Sun}, Xiang Gong, Amir Kavyan Ziabari, Leiming Yu, Xiangyu Li, Saoni Mukherjee, Carter McCardwell, Alejandro Villegas, and David Kaeli. 2016. \pubtitle{Hetero-Mark, a Benchmark Suite for CPU-GPU Collaborative Computing}. In 2016 IEEE International Symposium on Workload Characterization (IISWC '16). IEEE, 1–10.  https://doi.org/10.1109/IISWC.2016.7581262[Acceptance rate $\approx$ 30.4\%]}
        
        
        \cvpublication{\selfname{Yifan Sun}, Chisheng Liang, Steven Sutherland, Casper Harteveld, and David Kaeli. 2016. \pubtitle{Modeling Player Decisions in a Supply Chain Game}. In 2016 IEEE Conference on Computational Intelligence and Games (CIG '16). IEEE, 1–8.  https://doi.org/10.1109/CIG.2016.7860444 [Acceptance rate unknown]}
        
        \cvpublication{Saoni Mukherjee, \selfname{Yifan Sun}, Paul Blinzer, Amir Kavyan Ziabari, and David Kaeli. 2016. \pubtitle{A Comprehensive Performance Analysis of HSA and OpenCL 2.0}. In 2016 IEEE International Symposium on Performance Analysis of Systems and Software (ISPASS '16). IEEE, 183–193.  https://doi.org/10.1109/ISPASS.2016.7482093 [Acceptance rate $\approx$ 35.1\%]}
        
        \cvpublication{Jithin Jagannath, Anu Saji, Hovannes Kulhandjian, \selfname{Yifan Sun}, Emrecan Demirors, and Tommaso Melodia. 2013. \pubtitle{A hybrid MAC protocol with channel-dependent optimized scheduling for clustered underwater acoustic sensor networks}. In Proceedings of the 8th International Conference on Underwater Networks \& Systems (WUWNet '13). Association for Computing Machinery, New York, NY, USA, Article 3, 1–8. https://doi.org/10.1145/2532378.2532382 [Acceptance rate $=$ 20.0\%]}
        
        \cvpublication{\faTrophy \hspace{1pt}  \selfname{Yifan Sun} and Tommaso Melodia. 2013. \pubtitle{The Internet Underwater: an IP-compatible protocol stack for commercial undersea modems}. In Proceedings of the 8th International Conference on Underwater Networks \&; Systems (WUWNet '13). Association for Computing Machinery, New York, NY, USA, Article 37, 1–8. \\https://doi.org/10.1145/2532378.2532407 [Acceptance rate $=$ 20.0\%]}
        
    \end{cvpublications}

\cvsubsection{Journals}

    \begin{cvpublications}

    \cvpublication{Wenhan Lyu, Shuang Zhang, Tingting Chung, \selfname{Yifan Sun}, and Yixuan Zhang. 2025. \pubtitle{Understanding the practices, perceptions, and (dis)trust of generative AI among instructors: A mixed-methods study in the U.S. higher education}. Computers and Education: Artificial Intelligence 8 (2025), 100383.  https://doi.org/10.1016/j.caeai.2025.100383}

    \cvpublication{Shaoyu Wang, Hang Yan, Katherine E. Isaacs, and \selfname{Yifan Sun}. 2024. \pubtitle{Visual Exploratory Analysis for Designing Large-Scale Network-on-Chip Architectures: A Domain Expert-Led Design Study}. IEEE Transactions on Visualization and Computer Graphics 30, 4 (2024), 1970–1983.  https://doi.org/10.1109/TVCG.2023.3337173}

    \cvpublication{Shi Dong, \selfname{Yifan Sun}, Nicolas Bohm Agostini, Elmira Karimi, Daniel Lowell, Jing Zhou, José Cano, José L. Abellán, and David Kaeli. 2021. \pubtitle{Spartan: A Sparsity-Adaptive Framework to Accelerate Deep Neural Network Training on GPUs}. IEEE Transactions on Parallel and Distributed Systems 32, 10 (2021), 2448–2463. \\  https://doi.org/10.1109/TPDS.2021.3067825}

     \cvpublication{Rozhin Doroudi, Pedro Sequeira, Stacy Marsella, Ozlem Ergun, Rana Azghandi, David Kaeli, \selfname{Yifan Sun}, and Jacqueline Griffin. 2020. \pubtitle{Effects of trust-based decision making in disrupted supply chains}. PLOS ONE 15, 2 (February 2020), e0224761.  https://doi.org/10.1371/journal.pone.0224761}

     \cvpublication{Chen Li, \selfname{Yifan Sun}, Lingling Jin, Lingjie Xu, Zheng Cao, Pengfei Fan, David Kaeli, Sheng Ma, Yang Guo, and Jun Yang. 2019. \pubtitle{Priority-Based PCIe Scheduling for Multi-Tenant Multi-GPU Systems}. IEEE Computer Architecture Letters 18, 2 (2019), 157–160.  https://doi.org/10.1109/LCA.2019.2955119}

     \cvpublication{Amir Kavyan Ziabari, \selfname{Yifan Sun}, Yenai Ma, Dana Schaa, José L. Abellán, Rafael Ubal, John Kim, Ajay Joshi, and David Kaeli. 2016. \pubtitle{UMH: A Hardware-Based Unified Memory Hierarchy for Systems with Multiple Discrete GPUs}. ACM Trans. Archit. Code Optim. 13, 4, Article 35 (December 2016), 25 pages. https://doi.org/10.1145/2996190}

     \cvpublication{Abdulla K. Al-Ali, \selfname{Yifan Sun}, Marco Di Felice, Jarkko Paavola, and Kaushik R. Chowdhury. 2015. \pubtitle{Accessing Spectrum Databases Using Interference Alignment in Vehicular Cognitive Radio Networks}. IEEE Transactions on Vehicular Technology 64, 1 (2015), 263–272.  https://doi.org/10.1109/TVT.2014.2318837}

     \cvpublication{\selfname{Yifan Sun} and Kaushik R. Chowdhury. 2014. \pubtitle{Enabling Emergency Communication Through a Cognitive Radio Vehicular Network.} IEEE Communications Magazine 52, 10 (2014), 68–75.  https://doi.org/10.1109/MCOM.2014.6917404}

    \end{cvpublications}
    

\cvsubsection{Books}
    \begin{cvpublications}
        \cvpublication{\selfname{Yifan Sun}, \uwave{Sabila Al Jannat}, Trinayan Buruah, and David Kaeli. 2025. \pubtitle{\href{https://www.amazon.com/Accelerated-Computing-HIP-Yifan-Sun/dp/B0F4F3F211/}{Accelerated Computing with HIP: Second Edition.}} ISBN:979-8218107444.}

        \cvpublication{\selfname{Yifan Sun}, Trinayan Buruah, and David Kaeli. 2022. \pubtitle{\href{https://www.amazon.com/Accelerated-Computing-HIP-Yifan-Sun/dp/B0BQQ18HGP/}{Accelerated Computing with HIP}}. ISBN:979-8218107444.}
    \end{cvpublications}


\cvsubsection{Translation of My Books}
    \begin{cvpublications}
        \cvpublication{\selfname{Ифань Сун}, Тринайан Баруа, Дэвид Каэли.2024.\pubtitle{ВЫСОКОПРОИЗВОДИТЕЛЬНЫЕ ВЫЧИСЛЕНИЯ С ПОМОЩЬЮ HIP} (The Russian translation of the book Accelerated Computing with HIP, as part of the Supercomputing Education Series), Moscow University Press.}
    \end{cvpublications}
    

\cvsubsection{Book Chapters}
    
    \begin{cvpublications}
        \cvpublication{Shih-Hao Hung, Thomas B. Jablin, \selfname{Yifan Sun}, Rafael Ubal, and David Kaeli. 2015. \pubtitle{HSA Simulators}. A book chapter in Heterogeneous System Architecture: Practical Applications for Industry, 1st edition, Elsevier.}
    
    \end{cvpublications}

    
\cvsubsection{Patents}

    \begin{cvpublications}
        \cvpublication{Junping Zhao, \selfname{Yifan Sun}. Layne Peng, Jie Bao, Kun Wang. (Jan. 2021). \pubtitle{Intelligent data coordination for accelerated computing in cloud environment}. Patent No. US 10,891,156, Filed Apr 26, 2017, Issued Jan 12, 2021.}
        
        \cvpublication{\selfname{Yifan Sun}, Layne Peng, Robert A. Lincourt JR., John Cardente, and Junping Zhao. (Jun. 2019). \pubtitle{Managing access to a resource pool of graphics processing units under fine grain control}. Patent No. US 10,262,390, Filed Apr 14, 2017, Issued Jun 27, 2019.}
        
        \cvpublication{Junping Zhao, Layne Peng, Jie Bao, Kun Wang, and \selfname{Yifan Sun}. (Apr. 2019).  \pubtitle{Checkpointing for GPU-as-a-Service in Cloud Computing Environment}, Patent No. US 10,275,851, Filed Apr 25, 2017, Issued Apr 30, 2019.}
        
        \cvpublication{\selfname{Yifan Sun}, Layne Peng, Robert A. Lincourt JR., John Cardente, John S Harwood. (Oct. 2018). \pubtitle{Queue-based GPU Virtualization and Management System}. Patent No. US 10,109,030, Filed Dec 27, 2016, Issued Oct 23, 2018.}
    \end{cvpublications}

\cvsubsection{Workshop or Poster Publications}

    \begin{cvpublications}
        \cvpublication{\uwave{Daoxuan Xu}, Le Xu, Jie Ren, \selfname{Yifan Sun}. 2025.  \pubtitle{Exploring the Wafer-Scale GPUs}. The 17th Workshop on General Purpose Processing using GPU~(GPGPU 2025).}

        \cvpublication{Nicolás Meseguer, \selfname{Yifan Sun}, Michael Pellauer, José L. Abellán and Manuel E. Acacio. 2025.  \pubtitle{ACTA: Automatic Configuration of the Tensor Memory Accelerator for High-End GPUs}. The 17th Workshop on General Purpose Processing using GPU~(GPGPU 2025).}
    
        \cvpublication{\uwave{Chris Thames}, \selfname{Yifan Sun}. 2024.  \pubtitle{A Survey of Artificial Intelligence Approaches to Safety and Mission-Critical Systems}. The 24th Integrated Communications, Navigation and Surveillance Conference~(ICNS 2024).}
        
        \cvpublication{\uwave{Ying Li}, Yuhui Bao, Pranav Vaid, Gongyu Wang, Adwait Jog, Darius Bunandar, Ajay Joshi, \selfname{Yifan Sun}. 2023.  \pubtitle{TraceSim: a Lightweight Simulator for Large-Scale DNN Workloads on Multi-GPU Systems}. The First Workshop on Computer Architecture Modeling and Simulation~(CAMS 2023).}

        \cvpublication{Ali Mosallaei, Katherine Isaacs, \selfname{Yifan Sun}. 2023.  \pubtitle{Looking into the Black Box: Monitoring Computer Architecture Simulations in Real-Time with AkitaRTM}. The First Workshop on Computer Architecture Modeling and Simulation~(CAMS 2023).}
    
        \cvpublication{\uwave{Ying Li}, \selfname{Yifan Sun}, Adwait Jog. 2023.  \pubtitle{A Regression-based Model for End-to-End Latency Prediction for DNN Execution on GPUs}. 2023 IEEE International Symposium on Performance Analysis of Systems and Software~(ISPASS 2023).}
        
        \cvpublication{\uwave{Chris Thames}, Hang Yan, \selfname{Yifan Sun}. 2022.  \pubtitle{Understanding Wafer-Scale GPU Performance using an Architectural Simulator}. The 14th Workshop on General Purpose Processing using GPU~(GPGPU 2022).}
    
        \cvpublication{Yixuan Zhang, \selfname{Yifan Sun}, Sumit Barua, Enrico Bertini, and Andrea Grimes Parker. 2020.  \pubtitle{Mapping the Landscape of COVID-19 Crisis Visualizations}. Visualization for Communication (VisComm).}
    
    \end{cvpublications}

\cvsubsection{Preprints}

    \begin{cvpublications}

        \cvpublication{Saiful A. Mojumder, \selfname{Yifan Sun}, Leila Delshadtehrani, Yenai Ma, Trinayan Baruah, José L. Abellán, John Kim, David Kaeli, Ajay Joshi. 2020. \pubtitle{MGPU-TSM: A Multi-GPU System with Truly Shared Memory}. arXiv preprint arXiv:2008.02300.}
    
        \cvpublication{Saiful A. Mojumder, \selfname{Yifan Sun}, Leila Delshadtehrani, Yenai Ma, Trinayan Baruah, José L. Abellán, John Kim, David Kaeli, Ajay Joshi. 2020. \pubtitle{HALCONE : A Hardware-Level Timestamp-Based Cache Coherence Scheme for Multi-GPU Systems}. arXiv preprint arXiv:2007.04292.}
    
        \cvpublication{\selfname{Yifan Sun}, Nicolas Bohm Agostini, Shi Dong, and David Kaeli. 2019. \pubtitle{Summarizing CPU and GPU Design Trends with Product Data}. arXiv preprint arXiv:1911.11313.}
    
        \cvpublication{\selfname{Yifan Sun}, Trinayan Baruah, Saiful A Mojumder, Shi Dong, Rafael Ubal, Xiang Gong, Shane Treadway, Yuhui Bao, Vincent Zhao, José Luis Abellán, John Kim, Ajay Joshi, and David Kaeli. 2019. \pubtitle{MGSim+MGMark: A Framework for Multi-GPU System Research}. arXiv preprint arXiv:1811.02884.}
    
    \end{cvpublications}