\cvsection{Talks and Tutorials}

\begin{cvpublications}

\cvpublication{\pubtitle{User-Friendly Tools in Akita 3.0} \\ The 2nd Workshop on Computer Architecture Modeling and Simulation (CAMS '24). November 2024.}


\cvpublication{\pubtitle{On the Human Side of Computer Architecture, Towards Explainable Architecture} \\
North Carolina State University. October 2024.}

\cvpublication{\pubtitle{Towards Building Explainable Computer Architecture} \\
Lehigh University. Feb 2023.}

\cvpublication{\pubtitle{MGPUSim: A One-Stop Solution for GPU Architecture Simulation} \\
The 2020 International Conference on High Performance Computing \& Simulation
(HPCS '20). Jan 2021.}


\cvpublication{\pubtitle{MGPUSim: A High-Flexibility, High-Performance, Multi-GPU Simulator} \\
Alibaba. July 2020.}

\cvpublication{\pubtitle{Exploring Multi-GPU Simulation and Visual Profiling with MGPUSim} \\
With José L. Abellán, Trinayan Baruah, and David Kaeli. Tutorial at ISCA 2020. May 2020.}

\cvpublication{\pubtitle{Collaborative Heterogeneous Computing} \\ 
William \& Mary. March 2020.\\
University of California, Santa Cruz. March 2020. \\
University of Pittsburgh. March 2020.\\
University of Central Florida. March 2020.
}
\cvpublication{\pubtitle{Tutorial on the Akita Simulator Framework and MGPUSim} \\
With Trinayan Baruah, Shi Dong, and David Kaeli. Tutorial at HPCA 2020. February 2020.}
\cvpublication{\pubtitle{Research in the NUCAR
Laboratory at Northeastern University} \\
FutureWei. With David Kaeli. July 2019.}
\cvpublication{\pubtitle{MGSim: a Flexible High-Performance Simulator for Multi-GPU Systems} \\
International Workshop on OpenCL (IWOCL). May 2019.}
\cvpublication{\pubtitle{AKITA: A Go-Based Computer Architecture Simulator Framework} \\
Google.  May 2019.}
\cvpublication{\pubtitle{Enabling Multi-GPU High Performance Computing with Memory System Design} \\
Lighting talk at Boston University Red Hat Collaboratory.  February 2019.}
\cvpublication{\pubtitle{Benchmarking the New Unified Memory of CUDA 8} \\
With Frank Zhao. GTC 2017 San Jose. August 2017.}
\cvpublication{\pubtitle{Multi2Sim 5.0} \\
Tutorial at IISWC 2016. September 2016.}

\end{cvpublications}